Papers

### 2025-08-01 index.qmd
add new preprint info

@@

<font color="#d08770">[April 22 2025].</font> **Announcement**. The application period for practicum, project, or thesis positions in the lab for the 2025-26 academic year is now closed.

<font color="#d08770">[March 03 2025].</font> **New Preprint**. Lalli M, Al Afif N, Tang J, Hasan H, Dissanayake E, Sussman V, Lokesh R, Rathwell S, Cashaback JGA, & Carter MJ. Preferences for costly cooperation are highly individualized. *PsyAr$\chi$iv*. [https://doi.org/10.31234/osf.io/3qaeu_v3](https://doi.org/10.31234/osf.io/3qaeu_v3){target="_blank"}

>>>>

<font color="#d08770">[July 31 2025].</font> **New Preprint**. Sullivan SR, Buggeln JH, Calalo JA, Ngo TT, Semrau JA, Carter MJ, & Cashaback JGA. Involuntary feedback responses reflect a representation of partner actions. *bioR$\chi$iv*. [https://doi.org/10.1101/2025.07.29.667240](https://doi.org/10.1101/2025.07.29.667240){target="_blank"}

@@

### 2025-08-01 papers.qmd
add new preprint info

- Lalli, M., Al Afif, N., Tang, J., Hasan, H., Dissanayake, E., Sussman, V., Lokesh, R., Rathwell, S., Cashaback, JGA., & Carter, MJ. Preferences for costly cooperation are highly individualized. *PsyAr$\chi$iv*. --- [{{< ai doi >}}](https://doi.org/10.31234/osf.io/3qaeu_v3){target="_blank" style="color: inherit;"}

>>>>

- Sullivan SR., Buggeln JH., Calalo JA., Ngo TT., Semrau JA., Carter MJ., & Cashaback JGA.. Involuntary feedback responses reflect a representation of partner actions. *bioR$\chi$iv*. --- [{{< ai doi >}}](https://doi.org/10.1101/2025.07.29.667240){target="_blank" style="color: inherit;"}

- Lalli, M., Al Afif, N., Tang J., Hasan H., Dissanayake E., Sussman V., Lokesh R., Rathwell S., Cashaback JGA., & Carter MJ. Preferences for costly cooperation are highly individualized. *PsyAr$\chi$iv*. --- [{{< ai doi >}}](https://doi.org/10.31234/osf.io/3qaeu_v3){target="_blank" style="color: inherit;"}
